### 2006-03-15 paper/tags/JSS_20060315/systemfit_summary.tex
created tag for version submitted to the JSS on March 15, 2006
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@659 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\subsubsection*{Estimation methods}
In the future, we wish to include more sophisticated estimation
methods such as limited-information maximum likelihood (LIML),
full-information maximum likelihood (FIML), and generalized methods of
moments (GMM).

>>>>

\subsubsection*{Estimation methods}
In the future, we wish to include more sophisticated estimation
methods such as limited-information maximum likelihood (LIML),
full-information maximum likelihood (FIML), generalized methods of
moments (GMM) and spatial econometric methods.
